Equivalence Testing and the Second Generation P-Value

### 2018-07-30 sgpv_vs_TOST.Rmd

The second generation *p*-value (SGPV) is a new descriptive statistic that was recently proposed to "improve rigor, reproducibility and transparency across science" (Blume, McGowan, Dupont, & Greevy, (2018). The SGPV is 'the proportion of data-supported hypotheses that are also null hypotheses'. The researcher specify an equivalence range around the null hypothesis that specifies values that are considered practically equivalent to the null-hypothesis. The SGPV is the proportion of the  confidence interval (CI) around the observed effect estimate that falls within this equivalence range. If the CI falls completely inside the equivalence range the SGPV is 1, and if the CI falls completely outside the equivalence range the SGPV is 0.

@@

Blume, J. D., McGowan, L. D., Dupont, W. D., & Greevy, R. A. (2018). Second-generation *p*-values: Improved rigor, reproducibility, & transparency in statistical analyses. PLOS ONE, 13(3), e0188299. https://doi.org/10.1371/journal.pone.0188299

>>>>

The second generation *p*-value (SGPV) is a new descriptive statistic that was recently proposed to "improve rigor, reproducibility and transparency across science" (Blume, D'Agostino McGowan, Dupont, & Greevy, (2018). The SGPV is 'the proportion of data-supported hypotheses that are also null hypotheses'. The researcher specify an equivalence range around the null hypothesis that specifies values that are considered practically equivalent to the null-hypothesis. The SGPV is the proportion of the  confidence interval (CI) around the observed effect estimate that falls within this equivalence range. If the CI falls completely inside the equivalence range the SGPV is 1, and if the CI falls completely outside the equivalence range the SGPV is 0.

@@

Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., & Greevy, R. A. (2018). Second-generation *p*-values: Improved rigor, reproducibility, & transparency in statistical analyses. PLOS ONE, 13(3), e0188299. https://doi.org/10.1371/journal.pone.0188299
